Demanding resources: Converging perceptions of challenge and resource characteristics

### 2023-07-11 SIOP2024/SIOP2024convergence.Rmd
siop updates
number of items per scale issue (will resolve next meeting)

TukeyHSD(repmeas2)
library(car)

#levenes <- leveneTest(value ~ scale, data=analysis)

@@

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001. The only contrast approaching statistical significance via Tukey's HSD specification (*p* = .09) was the contrast between Physical Labor (*M* = 0.49) and Business and Financial Operations (*M* = 0.58).

>>>>

library(datarium)
library(tidyverse)
library(ggpubr)
library(rstatix)

tukeytest <- analysis %>% 
  pairwise_t_test(value ~ scale, paired = TRUE, 
                  p.adjust.method = "bonferroni"
                  )  
write.csv(tukeytest, "pairwisets.csv")
psych::describe.by(analysis$value, analysis$scale)

@@

>Note. This is all off because the "scales" have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001. The only contrasts not broaching statistical significance via Bonferonni-corrected pairwise t-tests were Work Output vs. Physical Work Conditions (*t* = -2.31), Interpersonal Relationships vs. Mental Processes (*t* = .18), and Information Input vs. Physical Work Conditions (*t* = 1.64). The largest contrasts were Interacting with Others vs. Work Output (*t* = 36.09) and Information Input vs. Interacting with Others (*t* = -34.38) and Mental Processes (*t* = -34.10)

### 2023-07-11 SIOP2024/SIOP2024convergence.tex
number of items per scale issue (will resolve next meeting)

@@

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.35 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001. The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58).

>>>>

\begin{verbatim}
## 
##  Descriptive statistics by group 
## group: Information
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 2.31 1.63      2    2.27 1.48   0   5     5 0.15    -1.07 0.07
## ------------------------------------------------------------ 
## group: Interact
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 7.57 4.21      7     7.5 4.45   0  17    17 0.13    -0.78 0.18
## ------------------------------------------------------------ 
## group: Interpersonal
##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
## X1    1 568 5.57 2.92      6     5.6 2.97   0  12    12 -0.06    -0.76 0.12
## ------------------------------------------------------------ 
## group: Mental
##    vars   n mean  sd median trimmed  mad min max range  skew kurtosis   se
## X1    1 568 5.55 2.9      6    5.66 2.97   0  10    10 -0.31    -0.92 0.12
## ------------------------------------------------------------ 
## group: Output
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 1.89 1.85      1     1.6 1.48   0   9     9  1.4     2.11 0.08
## ------------------------------------------------------------ 
## group: Physical
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 2.12 2.79      1    1.56 1.48   0  17    17 1.98     4.68 0.12
## ------------------------------------------------------------ 
## group: Structural
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 4.15 2.15      4    4.11 2.97   0  10    10  0.2    -0.52 0.09
\end{verbatim}

@@

\begin{quote}
Note. This is all off because the ``scales'' have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
\end{quote}

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.35 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001. The only contrasts not broaching statistical significance via Bonferonni-corrected pairwise t-tests were Work Output vs.~Physical Work Conditions (\emph{t} = -2.31), Interpersonal Relationships vs.~Mental Processes (\emph{t} = .18), and Information Input vs.~Physical Work Conditions (\emph{t} = 1.64). The largest contrasts were Interacting with Others vs.~Work Output (\emph{t} = 36.09) and Information Input vs.~Interacting with Others (\emph{t} = -34.38) and Mental Processes (\emph{t} = -34.10)
